Secure Composition \\ of Robust and Optimising Compilers

### 2023-10-11 esop/main.tex
Make sure text defines poison tags

$\Ltrg$ extends the syntax presented earlier (\Cref{subsec:cs:defs}) with dynamic typechecks ($\trg{\lhast{\expr}{\type}}$) and a way to inspect poison tags ($\trg{\lispoisoned{x}}$) in the metadata of pointers.
For valid pointers ($\trg{\poisonless}$) bound to variable $\trg{x}$, the check $\trg{\lispoisoned{x}}$ yields $\trg{1}$.
If the array bound to $\trg{x}$ was deallocated, i.e., has been poisoned ($\trg{\poisoned}$), the check $\trg{\lispoisoned{x}}$ evaluates to $\trg{0}$.
Dynamic typechecks $\trg{\lhast{\expr}{\type}}$ match on $\trg{\expr}$ and evaluate to $\trg{0}$ if the term is of type $\trg{\type}$ and $\trg{1}$ otherwise.
The projection $\msfilterL{\trg{\trace}}$ is equal to $\msfilterLtms{\src{\trace}}$.

>>>>

$\Ltrg$ extends the syntax presented earlier (\Cref{subsec:cs:defs}) with dynamic typechecks ($\trg{\lhast{\expr}{\type}}$).
The pointers carry poison tags, which signify a pointer being allocated ($\trg{\poisoned}$) or freed ($\trg{\poisonless}$). 
The syntax of $\Ltrg$ is extended further with a way to inspect whether a pointer is invalid ($\trg{\lispoisoned{x}}$).
Dynamic typechecks $\trg{\lhast{\expr}{\type}}$ match on $\trg{\expr}$ and evaluate to $\trg{0}$ if the term is of type $\trg{\type}$ and $\trg{1}$ otherwise.
The projection $\msfilterL{\trg{\trace}}$ is structurally equal to $\msfilterLtms{\src{\trace}}$.
